Verification of SE Formulas for Mediation Analysis

### 2024-05-01 notes/UQ Verification.tex
Fix mistake in a derivative for const, bin, fixed.

I set the sample size, $n$, to 100. Each regression coefficient is 1 and the residual standard deviation in both regression models is $0.2$. I use a single confounder and generate both it, $W$, and the exposure, $X$, as iid $\mathrm{N}(1,1)$. I generate $1000$ datasets, each with different values for $X$ and $W$.

@@

\begin{table}
    \centering
    \begin{tabular}{|c|c|c|}
        \hline
        Empirical & Mean Analytical & Median Analytical\\
        \hline
        0.0289 & 0.0288 & 0.0286\\
        \hline
    \end{tabular}
    \caption{Standard errors for estimated mediation effect with continuous response and mediation, fixed-effects.}
    \label{tab:SEs_cont_fix}
\end{table}

@@

\section{Continuous Response, Binary Mediation, Fixed-Effects}

@@

I repeated the analysis in Section \ref{tab:SEs_cont_fix}, this time with a binary mediator. Datasets are generated with $n=100$ observations, 3 confounders. Regression slopes are set to 1, and the intercept is set so that the expected linear predictor is approximately zero (this helps keep the number of 0s and 1s for $M$ approximately balanced). The residual variance for $Y$ is set to $0.2^2$.

@@

\begin{table}
    \centering
    \begin{tabular}{|c|c|c|}
        \hline
        Empirical & Mean Analytical & Median Analytical\\
        \hline
        0.0540 & 0.0584 & 0.0577\\
        \hline
    \end{tabular}
    \caption{Standard errors for estimated mediation effect with continuous response and binary mediation, fixed-effects.}
    \label{tab:SEs_cont_bin_fix}
\end{table}

>>>>

I set the sample size, $n$, to 1000. Each regression coefficient is 1 and the residual standard deviation in both regression models is $0.2$. I use a single confounder and generate both it, $W$, and the exposure, $X$, as iid $\mathrm{N}(1,1)$. I generate $1000$ datasets, each with different values for $X$ and $W$.

@@

\begin{table}
    \centering
    \begin{tabular}{|c|c|c|}
        \hline
        Empirical & Mean Analytical & Median Analytical\\
        \hline
        0.00833 & 0.00896 & 0.00895\\
        \hline
    \end{tabular}
    \caption{Standard errors for estimated mediation effect with continuous response and mediation, fixed-effects.}
    \label{tab:SEs_cont_fix}
\end{table}

@@

\section{Continuous Response, Binary Mediation, Fixed-Effects}
\label{sec:cont_bin_fix}

@@

I repeated the analysis in Section \ref{tab:SEs_cont_fix}, this time with a binary mediator. Datasets are generated with $n=1000$ observations, 3 confounders. Regression slopes are set to 1, and the intercept is set so that the expected linear predictor is approximately zero (this helps keep the number of 0s and 1s for $M$ approximately balanced). The residual variance for $Y$ is set to $0.2^2$.

@@

\begin{table}
    \centering
    \begin{tabular}{|c|c|c|}
        \hline
        Empirical & Mean Analytical & Median Analytical\\
        \hline
        0.0200 & 0.0203 & 0.0203\\
        \hline
    \end{tabular}
    \caption{Standard errors for estimated mediation effect with continuous response and binary mediation, fixed-effects.}
    \label{tab:SEs_cont_bin_fix}
\end{table}

\section{Binary Response, Binary Mediator, Fixed-Effects}

For my own future reference, I'm going to set out some notation here. $a$ and $b$ are the vectors of regression coefficients in a model for $M$ and $Y$ respectively, whether linear or logistic. We use $\eta$ and $\zeta$ for the linear predictors of $M$ and $Y$ respectively. In my code for Section \ref{sec:cont_bin_fix}, I used $\eta$, but didn't really need $\zeta$. Here I will. I use $\gamma$ for the total mediation effect. In the previous section (albeit only in my code), I used $\delta$ for $\bE(M | X=x+1) - \bE(M | X=x)$, although here I don't think I will need this quantity.

\section{Open Questions}

How does the standard error decompose between multiple responses with the same fixed covariates (i.e. $X$ and $W$), versus across replicated covariates? I can imagine how to do this, at least naively: do a bunch of analyses on each of a bunch of sets of covariates. Compute the average ``within-covariates'' variance and the average total variance. Compute the fraction of total variance due to response replication and, interestingly, one minus this fraction as a naive representation of the variance fraction due to covariate variability.
